Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-05-02 paper/paper.tex
feat(paper): Add Benjamin as author and state equal contribution
feat(paper): Add Flemisch paper citation and mention xSDK in the intro

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{TODO}
\author{
Max Hausch\autref{1},
Simon Hauser\autref{2}}

\institute{
\autlabel{1} \email{st175425@stud.uni-stuttgart.de}\\
\autlabel{2} \email{st148883@stud.uni-stuttgart.de}}

@@

Attempts were made to solve this situation by using Docker\footnote{\url{https://www.docker.com/}}, a software which describes software environments with the help of text files.
Those text files are made up of imperative commands which are run inside of containers, one layer at a time.
The result are several different layers which are all combines into a single output image that can be instantiated to a running container.
Docker images can be copied to different hosts and should then provide the same environment on different machines.
An issue that arises here, is that usually those images are based on one of the official Docker images\footnote{\url{https://docs.docker.com/trusted-content/official-images/}} all of which bring traditional package managers like \texttt{apt}.
When a user specifies to install the \texttt{python3} package with a traditional package manager today, the package manager could yield python3.8, whereas running the same command two months from now could yield python in the version 3.9.
This could potentially lead to different results when a user wants to only add a single dependency but has to rebuild the whole image, thus rendering it useless in terms of reproducibility.

>>>>

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{TODO}
\author{
Max Hausch\autref{1+},
Simon Hauser\autref{2+},
Benjamin Uekermann\autref{3}}

\institute{
\autlabel{1} \email{st175425@stud.uni-stuttgart.de}\\
\autlabel{2} \email{st148883@stud.uni-stuttgart.de}\\
\autlabel{3} \email{Benjamin.Uekermann@ipvs.uni-stuttgart.de}\\
\autlabel{+} These authors contributed equally to this work.}

@@

Attempts were made by scientists like Koch et al.~\cite{koch2023sustainable} to solve this situation by using Docker\footnote{\url{https://www.docker.com/}}, a software which describes software environments with the help of text files.
Those text files are made up of imperative commands which are run inside of containers, one layer at a time.
The result are several different layers which are all combines into a single output image that can be instantiated to a running container.
Docker images can be copied to different hosts and should then provide the same environment on different machines.
An issue that arises here, is that usually those images are based on one of the official Docker images\footnote{\url{https://docs.docker.com/trusted-content/official-images/}} all of which bring traditional package managers like \texttt{apt}.
When a user specifies to install the \texttt{python3} package with a traditional package manager today, the package manager could yield python3.8, whereas running the same command two months from now could yield python in the version 3.9.
This could potentially lead to different results when a user wants to only add a single dependency but has to rebuild the whole image, thus rendering it useless in terms of reproducibility.

Another ongoing effort, to at least make it easier to build scientific software, is made by the xSDK community~\cite{xSDK2023}.
The xSDK declares policies that a scientific software framework or library has to satisfy to be officially part of the xSDK ecosystem.
